Analysis of split plot design using lme4

### 2017-08-04 lme4_analysis.Rmd
Clean up comments in 03_preprocess_data.R
Simplify lmer analysis

```{r 2015_TShB_incidence}
library(lme4)
library(lsmeans)
TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
print(summary(TShB_inc_AUDPS), correlation = FALSE)

print(lsmeans(TShB_inc_AUDPS, list(pairwise ~ NRTE)), adjust = c("tukey"))
print(lsmeans(TShB_inc_AUDPS, list(pairwise ~ WMGT)), adjust = c("tukey"))
print(lsmeans(TShB_inc_AUDPS, list(pairwise ~ WMGT | NRTE)), adjust = c("tukey"))
```

@@

print(lsmeans(TShB_sev_AUDPS, list(pairwise ~ NRTE)), adjust = c("tukey"))
print(lsmeans(TShB_sev_AUDPS, list(pairwise ~ WMGT)), adjust = c("tukey"))
print(lsmeans(TShB_sev_AUDPS, list(pairwise ~ WMGT | NRTE)), adjust = c("tukey"))
```

@@

```{r 2015_LShB_severity}
LShB_sev_AUDPS <- lmer(LShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
print(summary(LShB_sev_AUDPS), correlation = FALSE)

@@

print(lsmeans(LShB_sev_AUDPS, list(pairwise ~ NRTE)), adjust = c("tukey"))
print(lsmeans(LShB_sev_AUDPS, list(pairwise ~ WMGT)), adjust = c("tukey"))
print(lsmeans(LShB_sev_AUDPS, list(pairwise ~ WMGT | NRTE)), adjust = c("tukey"))
```

@@

```{r 2016_TShB_incidence}
TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2016)
print(summary(TShB_inc_AUDPS), correlation = FALSE)

@@

print(lsmeans(TShB_inc_AUDPS, list(pairwise ~ NRTE)), adjust = c("tukey"))
print(lsmeans(TShB_inc_AUDPS, list(pairwise ~ WMGT)), adjust = c("tukey"))
print(lsmeans(TShB_inc_AUDPS, list(pairwise ~ WMGT | NRTE)), adjust = c("tukey"))
```

@@

```{r 2016_TShB_severity}
TShB_sev_AUDPS <- lmer(TShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2016)
print(summary(TShB_sev_AUDPS), correlation = FALSE)

@@

```{r 2016_LShB_severity}
LShB_sev_AUDPS <- lmer(LShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2016)
print(summary(LShB_sev_AUDPS), correlation = FALSE)

>>>>

```{r 2015_TShB_incidence}
library(lme4)
library(lsmeans)
TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT + NRTE + (1|REP), data = AUDPS_2015)
print(summary(TShB_inc_AUDPS), correlation = FALSE)

plot(TShB_inc_AUDPS)
qqnorm(residuals(TShB_inc_AUDPS))
qqline(residuals(TShB_inc_AUDPS))

print(lsmeans(TShB_inc_AUDPS, list(pairwise ~ NRTE)), adjust = c("tukey"))
print(lsmeans(TShB_inc_AUDPS, list(pairwise ~ WMGT)), adjust = c("tukey"))
```

@@

print(lsmeans(TShB_sev_AUDPS, list(pairwise ~ NRTE)), adjust = c("tukey"))
print(lsmeans(TShB_sev_AUDPS, list(pairwise ~ WMGT)), adjust = c("tukey"))
```

@@

```{r 2015_LShB_severity}
LShB_sev_AUDPS <- lmer(LShB_percent_AUDPS ~ WMGT + NRTE + (1|REP), data = AUDPS_2015)
print(summary(LShB_sev_AUDPS), correlation = FALSE)

@@

print(lsmeans(LShB_sev_AUDPS, list(pairwise ~ NRTE)), adjust = c("tukey"))
print(lsmeans(LShB_sev_AUDPS, list(pairwise ~ WMGT)), adjust = c("tukey"))
```

@@

```{r 2016_TShB_incidence}
TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT + NRTE + (1|REP), data = AUDPS_2016)
print(summary(TShB_inc_AUDPS), correlation = FALSE)

@@

print(lsmeans(TShB_inc_AUDPS, list(pairwise ~ NRTE)), adjust = c("tukey"))
print(lsmeans(TShB_inc_AUDPS, list(pairwise ~ WMGT)), adjust = c("tukey"))
```

@@

```{r 2016_TShB_severity}
TShB_sev_AUDPS <- lmer(TShB_percent_AUDPS ~ WMGT + NRTE + (1|REP), data = AUDPS_2016)
print(summary(TShB_sev_AUDPS), correlation = FALSE)

@@

```{r 2016_LShB_severity}
LShB_sev_AUDPS <- lmer(LShB_percent_AUDPS ~ WMGT + NRTE + (1|REP), data = AUDPS_2016)
print(summary(LShB_sev_AUDPS), correlation = FALSE)
